Difference-in-Differences with Spatial Spillovers\thanks{I am grateful to Taylor Jaworski, Adam McCloskey, Damian Clarke, Daniel Kaffine, Tania Barham, Alexander Bentz, James Flynn, Brach Champion, Hannah Denker, the CU Boulder Labor Economics Seminar, and the WEAI Conference}

### 2023-06-10 latex/paper/Spillover.tex
New draft

@@

\begin{align*}
    &\expec{Y_{i1} - Y_{i0} \ \mid \ D_i = 1} - \expec{Y_{i1} - Y_{i0} \ \mid \ D_i = 0, S_i = 0} \\
    &\quad\quad= \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0,0) \ \mid \ D_i = 1} - \expec{Y_{i1}(0, 0) - Y_{i0}(0,0) \ \mid \ D_i = 0} \\
    &\quad\quad= \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0,0) \ \mid \ D_i = 1} - \expec{Y_{i1}(0, 0) - Y_{i0}(0,0) \ \mid \ D_i = 1} \\
    &\quad\quad= \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0,0) - Y_{i1}(0, 0) + Y_{i0}(0,0) \ \mid \ D_i = 1} \\
    &\quad\quad= \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, 0) \ \mid \ D_i = 1} \\
    &\quad\quad\equiv \tau_{\text{total}},
\end{align*}
where the first equality comes from the fact that $S_i = 0$ implies $h_i(\vec{D}) = 0$, the second equality from parallel trends assumption (\ref{assumption:parallel-mod}), and the last by definition of the total effect.

@@

This section will give identification arguments for the total effect and spillover effects. First, note under \nameref{assumption:parallel_staggered}, we have 
\begin{align}
  \expec{Y_{it}(D_{it}, h_i(\vec{D}_t)) - \mu_i - \lambda_t \ | \ D_{it} = 1} 
  &= \expec{\tau_{it}(D_{it}, h_i(\vec{D}_t)) + \varepsilon_{it} \ | \ D_{it} = 1} \\
  &= \expec{\tau_{it}(D_{it}, h_i(\vec{D}_t)) \ | \ D_{it} = 1} \\
  &= \tau_{total}.
\end{align}
In the first stage, we estimate $\mu_i$ and $\lambda_t$ using observations with $D_{it}$ and $S_{it} = 0$. Unbiasedness/consistency follows from \nameref{assumption:local} and \nameref{assumption:no-anticipation_staggered} and the arguments of the appendix of \citet{Gardner_2021}.

A similar argument follows for spillover effects. Again, assuming \nameref{assumption:parallel_staggered}, we have 
\begin{align}
  \expec{Y_{it}(D_{it}, h_i(\vec{D}_t)) - \mu_i - \lambda_t \ | \ D_{it} = 0, S_{it} = 1} 
  &= \expec{\tau_{it}(D_{it}, h_i(\vec{D}_t)) + \varepsilon_{it} \ | \ D_{it} = 0, S_{it} = 0} \\
  &= \expec{\tau_{it}(D_{it}, h_i(\vec{D}_t)) \ | \ D_{it} = 0, S_{it} = 1}.
\end{align}

>>>>

\begin{remark}
  To highlight the importance of the modified parallel trends, we will compare the two estimands under the original \nameref{assumption:parallel}. The standard difference-in-differences estimate is biased from spillovers on nearby control units: 
  $$
    \expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 1 } - \expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 0 } = \tau_{\text{total}} - \tau_{\text{spill}}(0).
  $$
  On the other hand, using the $S_i = 0$ control group is biased by (potentially) non-parallel trends:
  \begin{align*}
    &\expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 1} - \expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 0, S_{i} = 0} \\
    &\quad\quad= \tau_{\text{total}} + (\expec{Y_{i1}(0, 0) - Y_{i0}(0,0) \ \mid \ D_i = 1} - \expec{Y_{i1}(0, 0) - Y_{i0}(0,0) \ \mid \ D_i = 0, S_i = 0}) 
  \end{align*}
  In this sense, there is a practical trade-off between two different sources of bias: spillover bias and the forming of potentially worse counterfactual conrol group.
\end{remark}

@@

\begin{align*}
    &\expec{Y_{i1} - Y_{i0} \ \mid \ D_i = 1} - \expec{Y_{i1} - Y_{i0} \ \mid \ D_i = 0, S_i = 0} \\
    &\quad\quad= \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0,0) \ \mid \ D_i = 1} - \expec{Y_{i1}(0, 0) - Y_{i0}(0,0) \ \mid \ D_i = 0, S_i = 0} \\
    &\quad\quad= \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0,0) \ \mid \ D_i = 1} - \expec{Y_{i1}(0, 0) - Y_{i0}(0,0) \ \mid \ D_i = 1} \\
    &\quad\quad= \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0,0) - Y_{i1}(0, 0) + Y_{i0}(0,0) \ \mid \ D_i = 1} \\
    &\quad\quad= \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, 0) \ \mid \ D_i = 1} \\
    &\quad\quad\equiv \tau_{\text{total}},
\end{align*}
where the first equality comes from the fact that $S_i = 0$ implies $h_i(\vec{D}) = 0$, the second equality from parallel trends assumption (\ref{assumption:parallel-mod}), and the last by definition of the total effect.

@@

This section will give identification arguments for the total effect and spillover effects. First, note under \nameref{assumption:parallel_staggered}, we have 
\begin{align*}
  \expec{Y_{it}(D_{it}, h_i(\vec{D}_t)) - \mu_i - \lambda_t \ | \ D_{it} = 1} 
  &= \expec{\tau_{it}(D_{it}, h_i(\vec{D}_t)) + \varepsilon_{it} \ | \ D_{it} = 1} \\
  &= \expec{\tau_{it}(D_{it}, h_i(\vec{D}_t)) \ | \ D_{it} = 1} \\
  &= \tau_{total}.
\end{align*}
In the first stage, we estimate $\mu_i$ and $\lambda_t$ using observations with $D_{it}$ and $S_{it} = 0$. Unbiasedness/consistency follows from \nameref{assumption:local} and \nameref{assumption:no-anticipation_staggered} and the arguments of the appendix of \citet{Gardner_2021}.

A similar argument follows for spillover effects. Again, assuming \nameref{assumption:parallel_staggered}, we have 
\begin{align*}
  \expec{Y_{it}(D_{it}, h_i(\vec{D}_t)) - \mu_i - \lambda_t \ | \ D_{it} = 0, S_{it} = 1} 
  &= \expec{\tau_{it}(D_{it}, h_i(\vec{D}_t)) + \varepsilon_{it} \ | \ D_{it} = 0, S_{it} = 0} \\
  &= \expec{\tau_{it}(D_{it}, h_i(\vec{D}_t)) \ | \ D_{it} = 0, S_{it} = 1}.
\end{align*}
